|

### 2019-05-02 rap/article.Rmd
update

---
title:  |
        | **Deaths and Disappearances in the Pinochet Regime: A New Dataset**
author: 
  - "Danilo Freire[^df]"
  - "John Meadowcroft[^jm]"
  - "David Skarbek[^ds]"
  - "Eugenia Guerrero[^eg]"
date: \today
thanks: "We thank Umberto Mignozzetti and Robert Myles McDonnell for their helpful comments. Replication materials and R source code are available at [`http://github.com/danilofreire/pinochet`](http://github.com/danilofreire/pinochet)."
abstract: "This article presents a georeferenced dataset on human rights violations in the Pinochet dictatorship in Chile. We coded the personal details of 2,398 victims named in the Chilean Truth Commission Report and added geographical coordinates for all identifiable atrocity locations. The dataset comprises 57 variables from 1973 to 1990 and is available as a stand-alone spreadsheet or as the `pinochet` package for `R`. As examples, we describe the major temporal and spatial patterns of the human rights abuses. We also discuss our coding procedures, show descriptive statistics, and conclude with suggestions for potential applications of the dataset."
keywords: "Chile, georeferenced event data, human rights, Pinochet, truth commission"
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    template: template.latex
---

@@

Our dataset comprises 2,398 observations and 57 variables. Each observation corresponds to a victim of the Pinochet regime and every individual has a unique id number. There are several variables describing the personal information of the victims, such as age, gender, nationality, occupation, and political affiliation if available. The data also feature geographical coordinates for a number of the incidents, as well as information about methods of torture and causes of death. Table 1 shows an example entry from our dataset.

@@

| Variable                | Sample          |
| :---------------------- | :-------------- |
| region                  | Taparacá        |
| id                      | 276             |
| page                    | 265             |
| start date              | 18/01/1974      |
| end date                | 18/01/1974      |
| last name               | Marques Agusto  |
| first name              | Nelson José     |
| minor                   | 0               |
| age                     | 31              |
| male                    | 1               |
| occupation              | Office worker   |
| victim affiliation      | Communist party |
| violence                | 1 (killed)      |
| method                  | 1 (gun)         |
| interrogation           | NA (unknown)    |
| torture                 | NA (unknown)    |
| mistreatment            | 1 (yes)         |
| perpetrator             | Military        |
| place                   | 5 (in public)   |
| start location          | Iquique         |
| latitude 1              | -20.23070       |
| longitude 1             | -70.13567       |
| place 2                 | 4 (in custody)  |
| location 2              | Pisagua prison  |
| latitude 2              | -19.59667       |
| longitude 2             | -70.21222       |

@@

| Violence         | _N_    |
| :--------------- | -----: |
| Killed           |   1331 |
| Disappeared      |    853 |
| Unresolved cases |     93 |
| Suicides         |      7 |
| Unknown          |        |

Table: Number of killings, disappearances, unresolved cases, and suicides

>>>>

---
title:  |
        | **Deaths and Disappearances in the Pinochet Regime: A New Dataset**
author: 
  - "Danilo Freire[^df]"
  - "John Meadowcroft[^jm]"
  - "David Skarbek[^ds]"
  - "Eugenia Guerrero[^eg]"
date: \today
thanks: "We thank Umberto Mignozzetti, Lucas Mingardi and Robert Myles McDonnell for their helpful comments. Replication materials and R source code are available at [`http://github.com/danilofreire/pinochet`](http://github.com/danilofreire/pinochet)."
abstract: "This article presents a georeferenced dataset on human rights violations in the Pinochet dictatorship in Chile. We coded the personal details of 2,398 victims named in the Chilean Truth Commission Report and added geographical coordinates for all identifiable atrocity locations. The dataset comprises XXXXXXXXXX variables from 1973 to 1990 and is available as a stand-alone spreadsheet or as the `pinochet` package for `R`. As examples, we describe the major temporal and spatial patterns of the human rights abuses. We also discuss our coding procedures, show descriptive statistics, and conclude with suggestions for potential applications of the dataset."
keywords: "Chile, georeferenced event data, human rights, Pinochet, truth commission"
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    template: template.latex
---

@@

Our dataset comprises 2,398 observations and XXXXXXXXX variables. Each observation corresponds to a victim of the Pinochet regime and every individual has a unique id number. There are several variables describing the personal information of the victims, such as age, gender, nationality, occupation, and political affiliation if available. The data also feature geographical coordinates for a number of the incidents, as well as information about methods of torture and causes of death. Table 1 shows an example entry from our dataset.

@@

| Variable                | Sample          |
| :---------------------- | :-------------- |
| id                      | 276             |
| page                    | 265             |
| start date              | 18/01/1974      |
| end date                | 18/01/1974      |
| last name               | Marques Agusto  |
| first name              | Nelson José     |
| minor                   | 0 (no)          |
| age                     | 31              |
| male                    | 1 (yes)         |
| occupation              | office worker   |
| victim affiliation      | communist party |
| violence                | killed          |
| method                  | gun             |
| interrogation           | NA (unknown)    |
| torture                 | NA (unknown)    |
| mistreatment            | 1 (yes)         |
| perpetrator             | military        |
| place                   | in public       |
| start location          | Iquique         |
| latitude 1              | -20.23070       |
| longitude 1             | -70.13567       |
| place 2                 | in custody      |
| location 2              | Pisagua prison  |
| latitude 2              | -19.59667       |
| longitude 2             | -70.21222       |

@@

| Violence         | _N_    |
| :--------------- | -----: |
| Killed           |   1331 |
| Disappeared      |    853 |
| Unresolved cases |     93 |
| Suicides         |      7 |
| Unknown          |    115 |

Table: Number of killings, disappearances, unresolved cases, and suicides.
